---
title: "p8105_hw6_lz2657"
author: Lingyu Zhang
date: Nov 18, 2018
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(modelr)
```

## Problem 1

First, read and tidy the raw data.
```{r problem1_read_tidy}
homicide_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide_data = 
  read.csv(url(homicide_url), stringsAsFactors = FALSE) %>% 
  janitor::clean_names() %>% 
  as_tibble()

homicide_data
```

Now create a city_state variable and a binary variable indicating whether the homicide is solved, and then omit some cities. Also modifiy victim_race to have categories white and non-white, with white as the reference category and make sure that victim_age is numeric.

```{r problem1_create_and_omit, warning=FALSE}
homicide_data = homicide_data %>%
  mutate(city_state = str_c(city, ", ", state)) %>%
  mutate(solved = as.numeric(disposition != "Closed without arrest" & disposition != "Open/No arrest")) %>%
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO" & city_state != "Tulsa, AL" & city_state != "PA, 40.461945") %>%
  mutate(victim_race = ifelse(victim_race == "White", "white","non-white"),
         victim_race = fct_relevel(victim_race, "white"), 
         victim_age = as.numeric(victim_age))
```

For Baltimore, fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors, and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r problem1_baltimore}
baltimore_log = homicide_data %>% 
  filter (city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

baltimore_log %>% 
  broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
  select(term, "adj odds ratio" = estimate, "CI: lower bound" = conf.low, 
           "CI: upper bound" = conf.high) %>% 
  knitr::kable(digits = 3)
```

Now run glm for each city, and extract the adjusted odds ratio and CI for solving homicides comparing non-white victims to white victims. 

```{r problem1_glm_cities}
logistic_function = function(df) {
  glm_fit = glm(solved ~ victim_age + victim_sex + victim_race, 
      data = df, family = binomial())
  
  glm_fit %>% 
    broom::tidy() %>% 
    mutate(odds_ratio = exp(estimate),
           conf_low = exp(estimate - 1.96 * std.error), 
           conf_high = exp(estimate + 1.96 * std.error))
}

homocide_odds_cities = homicide_data %>% 
  group_by(city_state) %>%
  nest() %>%
  mutate(log_models = map(data, logistic_function)) %>%
  select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon-white") %>% 
  select(city_state, odds_ratio, conf_low, conf_high)

homocide_odds_cities
```

Create a plot that shows the estimated ORs and CIs for each city. 

```{r problem1_plot}
homocide_odds_cities %>% 
  mutate(city_state = fct_reorder(city_state, desc(odds_ratio))) %>%
  ggplot(aes(x = city_state, y = odds_ratio, color = city_state)) + 
    geom_point() +
    geom_errorbar(aes(ymin = conf_low, ymax = conf_high, width = 0.2)) +
    theme(axis.text.x = element_text(angle = 60, hjust = 1), legend.position = "none") + 
    labs(
        title = "Adjusted Odds Ratios of Non-White to Whites for Solved Homicides",
        x = "City, State",
        y = "Adjusted Odds Ratio "
      )
```

## Problem 2

First, load and clean the data for regression analysis.

```{r problem2_load_clean}
birth_data = read_csv(file = "data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = recode(babysex, `1` = "male", `2` = "female"),
         frace = recode(frace,  `1` = "white", `2` = "black", `3` = "asian", 
                        `4` = "puerto_rican", `8` = "other", `9` = "unknown"),
         mrace = recode(mrace,  `1` = "white", `2` = "black", `3` = "asian", 
                        `4` = "puerto_rican", `8` = "other" ),
         smoken = as.integer(smoken)
  )
```

There are no missing data in the dataset.

Then propose a regression model for birthweight and describe the modeling process and show a plot of model residuals against fitted values.

```{r problem2_regression}
btw_reg = function(df) {
  lm(bwt ~ bhead + blength + gaweeks, data = df)
}

btw_model = btw_reg(birth_data)
  
birth_data %>% 
  add_predictions(btw_model) %>% 
  add_residuals (btw_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
    geom_point(alpha = 0.2) +
  labs(
        title = "Residuals vs. Predicted Values",
        x = "Predicted Birthweight",
        y = "Residuals"
      )
```

Now compare the model to two others in terms of the cross-validated prediction error.

```{r problem2_compare_models}
btw_model_main = function(df) {
  lm(bwt ~ blength + gaweeks, data = df)
}

btw_model_inter = function(df) {
  lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + 
       blength * babysex + bhead * blength * babysex, data = df)
}
```

```{r problem2_cross_validation}
set.seed(1)

birth_cv = crossv_mc(birth_data, 100) %>%
  mutate(btw_reg = map(train, btw_reg),
         btw_model_main = map(train, btw_model_main),
         btw_model_inter = map(train, btw_model_inter)) %>% 
  mutate(rmse_btw_reg = map2_dbl(btw_reg, test, ~rmse(model = .x, data = .y)),
         rmse_btw_model_main = map2_dbl(btw_model_main, test, ~rmse(model = .x, data = .y)),
         rmse_btw_model_inter = map2_dbl(btw_model_inter, test, ~rmse(model = .x, data = .y)))

birth_cv %>% 
  select(rmse_btw_reg, rmse_btw_model_main, rmse_btw_model_inter) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = recode(model, rmse_btw_model_hyp = "hypothesized", rmse_btw_model_sml = "main",
                        rmse_btw_model_int = "interaction"), 
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, color = model)) + 
  geom_violin() +
  theme(legend.position = "none") +
  labs(
        title = "Comparing birthweight models",
        x = "Model",
        y = "RMSE"
      )
```

It is shown in the figure that the hypothesized model has the least RMSE among all the three models. On the other hand, it's easier to interpret than the model with interaction. So the hypothesized one should be the best.